---
title: "Final Project R Reference"
author: "Bonnie Turek"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Reference Guide {.tabset .tabset-pills}


## Loading Data and Packages

## Data Structures
### c()

The function c() combines or concatenates its arguments into a vector (a 1-dimensional data structure consisting of 1 or more elements).

*   All of the elements must be of the same type.
*   I can’t combine character and numeric types in the same call to c()

Here’s two examples using numeric and character data types:
```{r}
## Create a vector of numbers:
num_vec  = c(1, 4, 8, 9, 13)

## Create a vector of characters:
char_vec = c("a", "fish", "data is cool")
```
I can show the contents of a vector by typing the name of the vector, or using the print() function.
```{r}
## Typing the name of the vector into the console prints the contents
num_vec
```
```{r}
## The print() function accomplishes the same task:
print(char_vec)
```


## Subsetting

## Numerical Data Exploration

## Graphical Data Exploration

## Distribuion Functions

